---
title: "week_3_lab_BinaryLogRegress"
author: "Kerry Nixon"
date: "1/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create a subset with only Adelie adn Chinstrp penguins

```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species))
```

Let's just datavis of these two species:
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm))+
  geom_point(aes(color = sex)) +
  facet_wrap(~species)
```

Binary Logistic Regression

- body mass
- flipper length
- penguin sex


```{r}
adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm + sex, 
                            data = adelie_chinstrap,
                            family = "binomial")
```

Take a look at the outcomes:
```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)
```

```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = flipper_length_mm)) +
  geom_jitter(aes(color = sex))
```

What are the actual probabilities of being Chinstrap for each of the exisiting obervations int he adelie_chinstrap dataframe?

```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response") # get fitted results in probabilities instead of logodds
```

Plotting the fitted probabilities

```{r}
ggplot(data = blr_fitted, aes(x = flipper_length_mm, y = .fitted)) +
  geom_point(aes(color = sex, pch = species)) +
  geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper length (mm)",
       y = "Probability of Outcome Chinstrap")
```

Plot model based on different variables:
```{r}
effect_plot(adelie_chinstrap_blr,
            pred = flipper_length_mm,
            y.lab = "Probability of Chinstrap",
            interval = TRUE)

effect_plot(adelie_chinstrap_blr,
            pred = body_mass_g,
            y.lab = "Probability of Chinstrap",
            interval = TRUE)
```

Whats the probabiltity that a femal penguins with a mass of 3410 g with a flipper legth of 192mm is a Chinstrap?

```{r}
ex_1 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female",
                           body_mass_g = 3410,
                           flipper_length_mm = 192),
                type = "response")

# 40% chance this is a Chinstrap penguin based on our model
```

